Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-01-11 paper/ms.tex
making solver picklable
adding astero figure to document

To demonstrate this method, we will use a very simple heuristic model based on
\dfmtodo{CITE} where the model PSD is given by a mixture of 6 components with
amplitudes and frequencies specified by $\nu_\mathrm{max}$, $\Delta \nu$, and
several nuisance parameters.
The first term is used to capture the granulation ``background'' using
\eq{granulation-psd} with two free parameters $S_g$ and $\omega_g$.
The remaining 5 terms are given by \eq{sho-psd} where $Q$ is a nuisance
parameter shared between terms and the frequencies are given by
\begin{eqnarray}
\omega_{0,\,j} = 2\,\pi\,(\nu_\mathrm{max} + j\,\Delta\nu + \epsilon)
\end{eqnarray}
and the amplitudes are given by
\begin{eqnarray}
S_{0,\,j} =
    \frac{A}{Q^2}\,\exp\left(-\frac{[j\,\Delta\nu + \epsilon]^2}{2\,W^2}\right)
\end{eqnarray}
where $j$ is an integer running from $-2$ to 2 and $\epsilon$, $A$, and $W$
are shared nuisance parameters.
This model could be easily extended to include small frequency splitting and
$\nu_\mathrm{max}$ and $\Delta \nu$ could be replaced by physical parameters
like $\log g$.

@@

>>>>

To demonstrate this method, we will use a very simple heuristic model based on
\dfmtodo{CITE} where the model PSD is given by a mixture of 6 components with
amplitudes and frequencies specified by $\nu_\mathrm{max}$, $\Delta \nu$, and
several nuisance parameters.
The first term is used to capture the granulation ``background'' using
\eq{granulation-psd} with two free parameters $S_g$ and $\omega_g$.
The remaining 5 terms are given by \eq{sho-psd} where $Q$ is a nuisance
parameter shared between terms and the frequencies are given by
\begin{eqnarray}
\omega_{0,\,j} = 2\,\pi\,(\nu_\mathrm{max} + j\,\Delta\nu + \epsilon)
\end{eqnarray}
and the amplitudes are given by
\begin{eqnarray}
S_{0,\,j} =
    \frac{A}{Q^2}\,\exp\left(-\frac{[j\,\Delta\nu + \epsilon]^2}{2\,W^2}\right)
\end{eqnarray}
where $j$ is an integer running from $-3$ to 3 and $\epsilon$, $A$, and $W$
are shared nuisance parameters.
This model could be easily extended to include small frequency splitting and
$\nu_\mathrm{max}$ and $\Delta \nu$ could be replaced by physical parameters
like $\log g$.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/astero-11615890-comparisons.pdf}
\caption{A comparison between the empirical PSD and the posterior inference of
the PSD as a mixture of stochastically driven simple harmonic oscillators.
(top) The periodogram of the \kepler\ light curve for KIC~11615890 computed
    on the full four year baseline of the mission.
    The light gray curve shows the raw periodogram and the black curve has
    been smoothed with a Gaussian filter with \dfmtodo{SOME WIDTH}.
(middle) The same periodogram computed using about a month of data.
(bottom) The inferred power spectrum under the mixture of SHOs model described
    in the text.
    The black line shows the median of posterior PSD and the gray contours
    show the 68\% credible region.
    \figurelabel{astero}}
\end{center}
\end{figure}

\subsection{Stellar rotation}

For many stars it is possible
